---
title: "p8105_hw1_co2554 for Camille"
author: "Camille Okonkwo"
due date: "2023-09-23"
output: github_document
---

Let's load up the `moderndive` library and open the `early_january_weather` dataset. 

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(moderndive)
data("early_january_weather")
```

# Problem 1

The `early_january_weather` dataset contains weather statistics between 01/01/2013-01/15/2013 at EWR (`origin`). Every hour, the `temp`, `dewp`, `humid`, `wind_speed`, `wind_gust`, `precip`, `pressure`, and `visib` are noted. There are   `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns, and the average temperature during this time is `r mean(early_january_weather[["temp"]])`.

### Let's make a scatterplot of `temp`(y) vs. `time_hour`(x).

```{r, results = FALSE}
data.frame("early_january_weather")
x = early_january_weather[["time_hour"]]
y = early_january_weather[["temp"]]

ggplot(early_january_weather, aes(x = x, y = y, color = humid)) + geom_point()
```

```{r, echo = FALSE}
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

`time_hour` and `temp` appear have a positively correlated relationship. As the `time_hour` increases, `temp` also increases.

# Problem 2

### Let's create a dataframe with random variables.

```{r}
set.seed(12345)

random_df = tibble(
  norm_samp = rnorm(10, sd =1),
  vec_logical = norm_samp > 0,
  vec_char = c("Camille", "is", "the", "best", "data", "science", "student", "at", "Columbia", "University"),
  vec_factor = factor(rep(c("sometimes", "always", "never"), length.out = 10))
)
```

#### Let's pull the variables we established above out the dataframe so we're able to take their means.

```{r random_df_means}
mean_norm_samp = mean(pull(random_df, norm_samp))
mean_vec_logical = mean(pull(random_df, vec_logical))
mean_vec_char = mean(pull(random_df, vec_char))
mean_vec_factor = mean(pull(random_df, vec_factor))
```

We are not able to take the mean of `vec_char` and `vec_factor` because they are not numeric variables. 

#### Let's convert all of the variables to numeric variables to see if we can solve this problem. 

```{r, results = FALSE}
as.numeric(pull(random_df, vec_logical))
as.numeric(pull(random_df, vec_char))
as.numeric(pull(random_df, vec_factor))
```

When we try to apply the `as.numeric` function to `vec_logical`, it is able to to translate as a binary condition. When applied to `vec_factor` it is able to be translated to a categorical variable with three levels. However, `vec_char` contains nominal datapoints, so it not able to be translated to a numerical variable because the nominal data points have no meaning. 
