---
title: "p8105_hw1_co2554 for Camille"
author: "Camille Okonkwo"
due date: "2023-09-23"
output: github_document
---

Let's load up the `moderndive` library and open the `early_weather_data` dataset. 

```{r}
library(tidyverse)
library(moderndive)
data("early_january_weather")
```

# Problem 1

The `early_january_weather` dataset contains weather statistics between 01/01/2013-01/15/2013 at EWR (`origin`). Every hour, the `temp`, `dewp`, `humid`, `wind_speed`, `wind_gust`, `precip`, `pressure`, and `visib` are noted. There are   `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns, and the average temperature during this time is `r mean(early_january_weather[["temp"]])`.

### Let's make a scatterplot of `temp`(y) vs. `time_hour`(x).

```{r}
data.frame("early_january_weather")
x = early_january_weather[["time_hour"]]
y = early_january_weather[["temp"]]

ggplot(early_january_weather, aes(x = x, y = y, color = humid)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)
```


